---
title: "Example: Flexible adjustment for a treatment effect"
author: "EXAMPLE_01"
student-id: "EXAMPLE_01"
design-method: "dml"
format:
  html:
    toc: true
    embed-resources: true
  docx:
    toc: true
  pdf:
    toc: true
  revealjs:
    slide-number: true
    scrollable: true
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
source("https://raw.githubusercontent.com/TheYongjinChoi/kapae2026-exercise/main/projects/design_lab/R/lab_helpers.R")

student_id <- "EXAMPLE_01"
method <- "dml"
research_title <- "Estimating the effect of programme participation on a continuous health outcome"
data_name <- "Illustrative national health survey"
data_description <- "Individual-level cross-sectional data with a binary programme indicator, continuous and categorical confounders, and a continuous health outcome. Nonlinear confounding is plausible."

outcome_type <- "continuous"
outcome_range <- c(0, 100)
n_continuous_predictors <- 8
n_binary_predictors <- 4
n_categorical_predictors <- 2
n_obs <- 1800
n_folds <- 5
max_missing_rate <- 0.08
seed <- 2026
submission_endpoint <- ""
course_key <- ""

spec <- build_spec_from_environment(environment())
analysis <- simulate_project(spec)
```

# 1. Research question and design

```{r}
#| results: asis
cat(project_overview_text(spec))
```

# 2. Data and expected structure

```{r}
#| results: asis
cat(data_structure_text(spec))
```

# 3. Methods

```{r}
#| results: asis
cat(methods_text(spec))
```

# 4. Main results

이 예시는 비선형 교란이 존재하는 상황을 의도적으로 만들어 **conventional OLS와 DML의 차이가 분명하게 보이도록** 구성합니다. 실제 연구에서는 이 차이 자체가 DML의 타당성을 보장하지 않으며, overlap, nuisance-model quality, cross-fitting stability를 함께 확인해야 합니다.

```{r}
#| results: asis
render_figure_list(make_main_figures(analysis, spec))
```

# 5. Interpretation

```{r}
#| results: asis
cat(interpretation_text(analysis, spec))
```

# Supplementary material

## A1. Missing records by variable

```{r}
knitr::kable(analysis$missingness, digits = 2)
```

## A2. Data-cleaning flow

```{r}
knitr::kable(analysis$cleaning_flow)
```

## A3. DML diagnostics

```{r}
#| results: asis
render_figure_list(make_supplement_figures(analysis, spec))
```

## A4. Required robustness checks

```{r}
#| results: asis
cat(supplement_checklist_text(spec))
```

## A5. Reproducibility

```{r}
sessionInfo()
```

# Render and submission

```{r}
#| eval: false
render_project_outputs(knitr::current_input())
submit_project(knitr::current_input(), endpoint = submission_endpoint, course_key = course_key)
```
