---
title: "Research Design Lab: Propensity-score matching"
author: "YongjinChoi"
student-id: "YongjinChoi"
design-method: "matching"
format:
  html:
    toc: true
    embed-resources: true
  docx:
    toc: true
  pdf:
    toc: true
    keep-tex: false
  revealjs:
    slide-number: true
    scrollable: true
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
source("https://raw.githubusercontent.com/TheYongjinChoi/kapae2026-exercise/main/projects/design_lab/R/lab_helpers.R")
student_id <- "YongjinChoi"
method <- "matching"
```

# 학생 입력 영역

이 파일은 **두 단계**로 작성합니다. 답변은 논문 초안이 아니라 수업에서 빠르게 공유할 연구설계 메모입니다. 각 서술형 항목은 가능하면 **1--3문장**으로 짧게 작성하세요. 수업 마지막 약 **30분 동안 서로의 설계를 함께 살펴보고 토론**합니다.

## 1단계. 연구 배경과 연구질문

```{r}
#| label: research-background
#| include: false

research_title <- "Association of healthcare-worker recommendation with parental vaccine confidence using propensity-score matching"

theoretical_background <- "Healthcare-worker recommendation is strongly related to vaccine attitudes but is not randomly distributed across caregivers."

research_need <- "Matching can construct a comparison group with similar observed pretreatment characteristics, making covariate balance and common support central to the analysis."

research_question <- "Among caregivers who received a healthcare-worker recommendation, how different is vaccine confidence compared with observably similar caregivers who did not receive one?"

expected_contribution <- "The exercise emphasises that a matched effect estimate is interpretable only after inspecting overlap, balance, matched-sample quality, and sensitivity to matching choices."
```

## 2단계. 방법론과 실제 데이터 구조 확인

여러분이 실제 연구에 사용할 데이터를 **직접 확인하거나 구체적으로 떠올려보며** 아래 질문에 답하세요. 이 질문들은 단순 입력란이 아니라, 선택한 방법론의 식별전략 또는 예측전략이 현재 데이터에서 가능한지를 점검하는 체크리스트입니다. **필수 질문에 답하기 어렵다면 그 방법론이 현재 데이터에 적절하지 않을 수 있습니다.**

```{r}
#| label: method-data-inputs
#| include: false

data_name <- "National caregiver vaccine confidence survey"
unit_of_observation <- "Caregiver"

outcome_var <- "vaccine_confidence_index"
outcome_label <- "Parental vaccine confidence"

covariate_names <- c("caregiver_age", "education", "income", "child_age", "prior_vaccination", "gov_trust", "healthcare_access", "region")
covariate_labels <- c("Caregiver age", "Education", "Household income", "Child age", "Prior child vaccination", "Trust in government", "Healthcare access", "Region")

treatment_var <- "hcw_recommendation"
treatment_label <- "Healthcare-worker recommendation"

covariate_timing_note <- "All matching covariates are defined using characteristics measured before or not caused by the recommendation exposure."

n_obs <- 2000
outcome_type <- "continuous"
outcome_range <- c(0, 10)
n_continuous_predictors <- 8
n_binary_predictors <- 4
n_categorical_predictors <- 2

estimand <- "ATT"
ps_method <- "matching"
caliper <- 0.2

max_missing_rate <- 0.08
seed <- 2026

submission_endpoint <- ""
course_key <- ""

spec <- build_spec_from_environment(environment())
```

# 1. Research background and question

```{r}
#| results: asis
cat(project_overview_text(spec))
```

# 2. Data-method compatibility check

```{r}
#| results: asis
cat(data_structure_text(spec))
cat(data_compatibility_text(spec))
```

# 3. Methods

```{r}
#| results: asis
cat(methods_text(spec))
```

# 4. Simulated analysis

아래 결과는 입력한 연구설계와 데이터 구조를 바탕으로 만든 **교육용 가상 결과**입니다. 실제 분석 결과가 아닙니다.

```{r}
#| label: simulate
analysis <- simulate_project(spec)
```

## Main results

```{r}
#| label: main-results
main_figures <- make_main_figures(analysis, spec)
render_figure_list(main_figures)
```

## Automatic basic interpretation

```{r}
#| results: asis
cat(interpretation_text(analysis, spec))
```

# Supplementary material

## Supplement 1. Missing records by variable

```{r}
knitr::kable(analysis$missingness, digits = 2)
```

## Supplement 2. Data-cleaning flow

```{r}
knitr::kable(analysis$cleaning_flow)
```

## Supplement 3. Full design-specific diagnostics and sensitivity analyses

```{r}
supp_figures <- make_supplement_figures(analysis, spec)
render_figure_list(supp_figures)
```

## Supplement 4. Required robustness and sensitivity checklist

```{r}
#| results: asis
cat(supplement_checklist_text(spec))
```

## Supplement 5. Reproducibility record

```{r}
sessionInfo()
```

# 5. Render outputs

```{r}
#| eval: false
render_project_outputs(knitr::current_input())
```

# Submission

```{r}
#| eval: false
submit_project(
  qmd_path = knitr::current_input(),
  endpoint = submission_endpoint,
  course_key = course_key
)
```
